---
title: "Plots of (bi-objective) LP/IP"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Set up 

```{r setup, include=FALSE}
library(knitr)
library(rgl)
knit_hooks$set(webgl = hook_webgl)
opts_chunk$set(
   #cache = TRUE,
   #echo = FALSE,
   #warning = FALSE,
   #message = FALSE,
   include = TRUE,
   fig.show = 'hold'
   )
options(width = 160)
```

Function for loading missing packages that install them if not already installed:

```{r}
#' Function for loading missing packages that install them if not already installed.
#'
#' @param packages String vector with package names
#'
#' @return NULL (invisible)
#' @export
#'
#' @examples loadPackages(c("MASS", "ggplot2", "tikzDevice"))
loadPackages <- function(packages) {
   newP <- packages[!(packages %in% installed.packages()[,"Package"])]
   if(length(newP)) install.packages(newP, repos = "http://cran.rstudio.com/")
   lapply(packages, library, character.only = TRUE)
   invisible(NULL)
}
loadPackages(c("geometry", "MASS", "ggplot2", "tikzDevice", "rgl", "ggrepel"))
source('functions3D.R')  # functions for plotting
```


## LP

Define the LP max/min coeff*x st. Ax<=b, x>=0

```{r}
A <- matrix(c(9,10,2,4,-3,2), ncol = 2, byrow = TRUE)
A
b <- c(90,27,3)
coeff <- c(7.75, 10)
```

Plot feasible region:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = rep("c", ncol(A)),
  crit = "max",
  faces = rep("c", ncol(A)),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = F,
  labels = NULL
  )
```

With optimum and labels:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = rep("c", ncol(A)),
  crit = "max",
  faces = rep("c", ncol(A)),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
```

Minimize:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = rep("c", ncol(A)),
  crit = "min",
  faces = rep("c", ncol(A)),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
```

Note return a ggplot so can e.g. add other labels:

```{r}
p <- plotPolytope(
  A,
  b,
  coeff,
  type = rep("c", ncol(A)),
  crit = "max",
  faces = rep("c", ncol(A)),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
p + xlab("x") + ylab("y")
```

## IP

IP model with LP faces:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = rep("i", ncol(A)),
  crit = "max",
  faces = rep("c", ncol(A)),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
```

IP model with IP faces:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = rep("i", ncol(A)),
  crit = "max",
  faces = rep("i", ncol(A)),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
```

## MIP

MIP model:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = c("c", "i"),
  crit = "max",
  faces = c("c", "i"),
  plotFaces = F,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
```

With faces:

```{r}
plotPolytope(
  A,
  b,
  coeff,
  type = c("i", "c"),
  crit = "max",
  faces = c("i", "c"),
  plotFaces = T,
  plotFeasible = T,
  plotOptimum = T,
  labels = "coord"
  )
```


## Bi-objective models

To plot these we need the `rgl` package. We define the model:

```{r, include=TRUE, echo=TRUE}
Ab <- matrix( c(
   2, 1, 1, 5,
   0, 2, -1, 3,
   1, -1, 2, 3
), nc = 4, byrow = TRUE)
A <- Ab[,1:3]
b <- Ab[,4]
# obj <- c(9,10,1)
# obj <- c(3,1,2)
# obj <- c(30,10,11)
obj <- c(3,1,1)  # 1D obj
obj2d <- matrix(c(3, 1, 0, 3, 1, 5), byrow = T, nrow = 2)
obj2d
```

Create 3D plot of the feasible region: (remember to run asymptote when you compile in LaTeX):

```{r, webgl=TRUE}
library(rgl)
load("view.RData")
view3d(userMatrix = view)
type <- c("i","c","c")
# create 3d plot in rgl
plotPolytope(A, b, coeff = obj, type = type,  plotFeasible = T, labels = "numb", plotOptimum = F, argsAxes3d = list(labels=F, tick = F), argsTitle3d=list(xlab = '$x_1$', ylab='$y_1$', zlab='$y_2$') )
```

Plot the solution in criterion space

```{r fig.show='asis'}
p <- plotCriterion2D(A, b, coeff = obj2d, type = type, labels = "numb", addTriangles = TRUE)
p
```

Let us try to make LaTeX pdf:

```{r, eval=FALSE}
# save the 3d plot in asy format in file polytope.tex
writeASY(outtype = "pdflatex", prc = F, title = "polytope")  # use prc = T if want an interactive 3D plot
rgl.quit() # close rgl

tikz(file = "mo.tex", standAlone=F, width = 7, height = 6)
p
dev.off()
```

Two LaTeX files have now been created. We have a look at them using the file ex.tex:

```{r}
writeLines(readLines(con = "main_mo.tex"))
```

The file must be compiled using PdfLaTeX -> Asymptote -> PdfLaTeX in TexStudio (added shortcut F10). Alternative we may do it using R:

```{r, eval=FALSE}
system(paste0("pdflatex.exe --shell-escape -synctex=1 -interaction=nonstopmode ", getwd(), "/main_mo.tex"))
system(paste0("asy.exe -globalwrite ", getwd(), "/main_mo-1.asy"))
system(paste0("pdflatex.exe --shell-escape -synctex=1 -interaction=nonstopmode ", getwd(), "/main_mo.tex"))
system(paste0('C:/"Program Files (x86)"/Adobe/"Acrobat Reader DC"/Reader/AcroRd32.exe ', getwd(), '/main_mo.pdf'))
```

Remove tempoary files:

```{r, eval=FALSE}
unlink(c("mo.tex", "ex-1.pdf", "*.asy", "*.aux", "polytope.tex", "*.log", "*.pre", "*.gz", "*tikz*") )
```

