---
title: "Distribution fitting"
author: "Lars Relund Nielsen"
date: "20 feb 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r}
#' Function for loading missing packages that install them if not already installed.
#'
#' @param packages String vector with package names
#'
#' @return NULL (invisible)
#' @export
#'
#' @examples loadPackages(c("MASS", "ggplot2", "tikzDevice"))
loadPackages <- function(packages) {
   newP <- packages[!(packages %in% installed.packages()[,"Package"])]
   if(length(newP)) install.packages(newP, repos = "http://cran.rstudio.com/")
   lapply(packages, library, character.only = TRUE)
   invisible(NULL)
}
```

## Find best distribution

We use the package `fitdistrplus` and an [example](https://stats.stackexchange.com/questions/132652/how-to-determine-which-distribution-fits-my-data-best):

```{r}
loadPackages(c("fitdistrplus", "logspline"))

x <- c(37.50,46.79,48.30,46.04,43.40,39.25,38.49,49.51,40.38,36.98,40.00,
38.49,37.74,47.92,44.53,44.91,44.91,40.00,41.51,47.92,36.98,43.40,
42.26,41.89,38.87,43.02,39.25,40.38,42.64,36.98,44.15,44.91,43.40,
49.81,38.87,40.00,52.45,53.13,47.92,52.45,44.91,29.54,27.13,35.60,
45.34,43.37,54.15,42.77,42.88,44.26,27.14,39.31,24.80,16.62,30.30,
36.39,28.60,28.53,35.84,31.10,34.55,52.65,48.81,43.42,52.49,38.00,
38.65,34.54,37.70,38.11,43.05,29.95,32.48,24.63,35.33,41.34)

descdist(x, discrete = FALSE)
```

The kurtosis and squared skewness of your sample is plottet as a blue point named "Observation". It seems that possible distributions include the Weibull, Lognormal and possibly the Gamma distribution.

Let's fit a Weibull distribution and a normal distribution:

```{r}
fitWeibull <- fitdist(x, "weibull")
plot(fitWeibull)
fitNorm <- fitdist(x, "norm")
plot(fitNorm)
```

Both look good but judged by the QQ-Plot, the Weibull maybe looks a bit better, especially at the tails. Correspondingly, the AIC of the Weibull fit is lower (`r fitWeibull$aic`) compared to the normal fit (`r fitNorm$aic`).




